---
title: How to echo all code chunks or specific named ones.
author: |-
  Shripad Sinari \
  shripad.sinari@gmail.com 
date: "`r Sys.Date()`"
output:
  pdf_document:
    fig_caption: yes
    keep_tex: yes

---

# Demo

In this demo we create a small mock report based on the mtcars dataset provided
in R. The goal is show how to use the knitr package to echo specific code chunks
to display code _at the end of the report_. We will echo a specific code chunk
which modifies the standard mtcars data frame and then echo _all_ code chunks in
this report as well.

This code chunk echo is achieved by using _ref.label_ option in the code chunk
and supplying the option with _name_ of the code chunk to be displayed as such.

The `all_labels` function return a character vector of all code chunk names. One
can then select the code chunk name to be displayed. To display all chunks just
supply the character vector returned by `all_labels` as value to _ref.label_ as
such

```{r LoadLib, echo = FALSE, eval = TRUE, message=FALSE, warning=FALSE, results = "hide"}

## Live in tidyverse.
library(tidyverse)

## we need this library to make mtcars a tibble.
library(dplyr)

## we need this library as it is not part of tidyverse.
library(knitr) 

## The following idea of wrapping code chunk options
## around the code chunk display is taken from:
## https://github.com/yihui/knitr-examples/blob/master/062-chunk-wrapper.Rmd

library(knitr)
knit_hooks$set(wrapper = function(before, options, envir) {
  if (before) {
    sprintf('    ```{r %s}\n', options$params.src)
  } else '    ```\n'
})

```

```{r modify_data, echo = FALSE, eval = TRUE, message=FALSE, warning=FALSE, results = "hide"}
## Clear any previous data.
rm(list = ls())
mtcars <- mtcars %>%
    rownames_to_column("cars") %>%
    mutate(make = sub("\\s.*", "", cars)
         , model = sub("^.*\\s", "", cars)) %>%
    as_tibble()

```

```{r display, echo = FALSE, eval = TRUE, message=FALSE, warning=FALSE,fig.pos="H", fig.path='plot-', dev='pdf', fig.ext='pdf', fig.width=8, fig.height=6, fig.cap = "Plot to display. End of mock demo."}

mtcars %>%
    ggplot(aes(mpg, disp)) +
    geom_point(aes(color = make, shape = factor(gear))) +
    guides(shape = guide_legend(title = "Gear")
         , color = guide_legend(title = "Car Company"))

```


\clearpage

# Code that modifies the mtcars data frame is displayed.

```{r modify_df, wrapper = TRUE, ref.label = all_labels()[grep("modify",all_labels())],echo = TRUE, eval = FALSE, message=FALSE, warning=FALSE, results = "hide"}

```

\clearpage

# All code chunks are displayed in a single view.

```{r allcode, wrapper = TRUE, ref.label = all_labels(),echo = TRUE, eval = FALSE, message=FALSE, warning=FALSE, results = "hide"}

```

\clearpage

# Reproducibility

```{r ssinfo, echo = FALSE, eval = TRUE, message=FALSE, warning=FALSE, results = "markup"}
sessionInfo()
```

